Paper Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-11 paper-plan/paper-plan.tex
Updated paper structure

There is some domain in which requires probabilistic planning. As FF-Replan and
RFF are about using deterministic planners in a probabilistic domain, we like
to see what's new and if we can find some holes that are still open.

@@

\section{Related works}

@@

\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}

@@

\subsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}

@@

\subsection{}

>>>>

We will focus on 2 of the current state of the art probabilistic planning
algorithms that apply determinization in probabilistic domains and criticize
the approaches by formulating a real-world domain as opposed to the IPPC
domains.  By comparing both approaches and analyzing other state of the art
work we will propose some adjustments which we will theoretically test in this
domain. If it is realistic, we will also try to create an empirical evaluation.

@@

@@

\subsubsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}

@@

\subsubsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}

@@

\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\ref{martin2013progressive}}

In this paper a probabilistic plan graph heuristic is described which computes
information about the interaction between actions and between propositions.
This information is used to find better relaxed plans to compute the
probability of success. This information guides a forward state space search
for high probability, non-branching seed plans. These plans are then used in
a planning and scheduling system that handles unexpected outcomes by runtime
replanning.

\subsubsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
